---
layout: post
title: "Bootstrapping with student stature"
author: "Trey Batey"
date: "2016-01-23"
categories: [anthropology, rstats]
tags: [bootstrap, stature]
---

Bootstrapping is a convenient method for testing the reliability of statistics from relatively small samples. In this post, I work through an example of bootstrapping using data on stature from anthropology students at LCC.

Before beginning, load some R packages into the workspace. 

```{r message=FALSE, warning=FALSE, results='hide'}
packs <- c("googlesheets", "ggplot2", "ggthemes", "dplyr", "broom", "tidyr")
lapply(packs, require, character.only = TRUE)
```

The data are stored in a Google Sheet, and the `googlesheets` package provides interoperability.

```{r}
# gs_auth()   # register the spreadsheet; line is commented b/c on first run, received warning/execution halted

mysheets <- gs_ls()   # create data frame of available spreadsheets

stature.sheet <- gs_title("AnthropometryStature")

stature <- stature.sheet %>% gs_read()
```

So, what do the data look like?

```{r}
str(stature)
summary(stature$stature)

ggplot(data = stature, aes(x = stature, fill = sex)) + geom_histogram(binwidth = 1, alpha = 0.5, position = "identity") + theme_bw()
```

Or, a density plot.

```{r}
ggplot(data = stature, aes(x = stature, fill = sex)) + geom_density(alpha = 0.5, position = "identity") + theme_bw()
```

There are only 24 observations. We could bootstrap this sample using some functions from the `dplyr` package.

```{r}
set.seed(1859)


boot.stature <- sample_n(stature, 10000, replace = TRUE)

ggplot(data = boot.stature, aes(x = stature, fill = sex)) + geom_density(alpha = 0.5, position = "identity") + theme_bw()
```
